Neural Textures make Better Simulators ``I can't believe it's not real!"

### 2022-06-12 CORL/example.tex
example.tex: Added module_translator.pdf into the latex doc
Commented out the citations section; which we don't need anymore.

	\begin{figure}[H]
		\begin{center}
			\includegraphics[width=400pt]{../images/learnable_textures.pdf}
		\end{center}
		\caption{
			This figure illustrates how the neural textures are calculated in figure \ref{fig:main_diagram}. They are fully differentiable, and represented continuously along the texture's U and V axes using fourier feature networks.
		}
		% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
		% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
		% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
		\label{fig:learnable_textures}
	\end{figure}
	s

@@

@@

Can't handle transparent objects. 
A limited number of objects can be learned at once before supervision is necessary with color loss (but there are workarounds).
Takes a long time to train.

@@

\section{Citations} 
\label{sec:citations}

Citations can be made using either \textbackslash citep\{\} or \textbackslash citet\{\}, depending on the appropriateness. To avoid the citation moving to the next line, it is often a good practice to replace the space before with a tilde (\~{}) character.
Example 1: ``CoRL is the best conference ever~\citep{fourier_feature_networks}.''
Example 2: ``\citet{fourier_feature_networks} proved, both theoretically and numerically, that CoRL is the best conference ever.''

>>>>

	\begin{figure}[H]
		\begin{center}
			\includegraphics[width=400pt]{../images/learnable_textures.pdf}
		\end{center}
		\caption{
			This figure illustrates how the neural textures are calculated in figure \ref{fig:main_diagram}. They are fully differentiable, and represented continuously along the texture's U and V axes using fourier feature networks.
		}
		% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
		% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
		% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
		\label{fig:learnable_textures}
	\end{figure}

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=200pt]{../images/module_translator.pdf}
	\end{center}
	\caption{
		A subset of figure \ref{fig:main_diagram} focusing on the image translation module $T$.
	}
	% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
	% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
	% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
	\label{fig:learnable_textures}
\end{figure}

@@

Can't handle transparent objects.

A limited number of objects can be learned at once before supervision is necessary with color loss (but there are workarounds).

Takes a long time to train.

@@

% \section{Citations} 
% \label{sec:citations}

% Citations can be made using either \textbackslash citep\{\} or \textbackslash citet\{\}, depending on the appropriateness. To avoid the citation moving to the next line, it is often a good practice to replace the space before with a tilde (\~{}) character.
% Example 1: ``CoRL is the best conference ever~\citep{fourier_feature_networks}.''
% Example 2: ``\citet{fourier_feature_networks} proved, both theoretically and numerically, that CoRL is the best conference ever.''
